Simulation Figures for Genome Biology (simulations)

### 2018-07-23 manuscript_figures/manuscript_figures_sims.Rmd
Look at higher FDR cutoffs for ASH unimodal sims

```{r, eval = FALSE}
for (ia in 1:10) {
    summary_file <- paste0("allres_alpha", 100*alpha, ".rds")
    if (!file.exists(summary_file)) {
        res_files <- list.files(path, "\\.rds$", full.names = TRUE)
        res <- lapply(res_files, function(x) {
            zz <- readRDS(x)
            zz <- plotsim_standardize(zz, alpha = alpha)
            zz <- dplyr::select(zz, rep, blabel, key, alpha, value)
            zz <- dplyr::group_by(zz, blabel, key, alpha)
            zz <- dplyr::summarize(zz,
                                   se = sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))),
                                   q10 = quantile(value, .1, na.rm = TRUE),
                                   q90 = quantile(value, .9, na.rm = TRUE),
                                   med_value = median(value, na.rm = TRUE),
                                   mean_value = mean(value, na.rm = TRUE),
                                   nNA = sum(is.na(value)))
            dplyr::ungroup(zz)
        })
        names(res) <- gsub("\\.rds$", "", basename(res_files))
        saveRDS(res, summary_file)
    }
}
```

@@

```{r}
res <- vector("list", 10)
for (ia in 1:10) {
    imethodset <- methodset
    imethodset[which(imethodset == "ihw")] <- paste0("ihw-a", sprintf("%02d", ia))
    ires <- readRDS(paste0("allres_alpha", ia, ".rds"))
    ires <- bind_rows(ires, .id = "setting")
    ires <- dplyr::mutate(ires, dist = gsub(".*?-benchmark-(.*)", "\\1", setting),
                         setting = gsub("(.*?)-benchmark-.*", "\\1", setting))
    ires <- dplyr::filter(ires, blabel %in% imethodset)
    ires <- dplyr::mutate(ires, blabel = gsub("(-a)(.*)", "", blabel))
    res[[ia]] <- ires
}
res <- bind_rows(res)
res <- dplyr::rename(res, Method = blabel)
res <- dplyr::mutate(res, Method = gsub("-df03", "", Method))
res <- dplyr::mutate(res, Method = factor(Method, levels = gsub("-df03", "", methodset)))
```

@@

noise_fdr <- dplyr::filter(res_noise, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ dist, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDP", labels = scales::percent) +
    ggtitle("Mean FDP Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

@@

```{r, fig.width = 18, fig.height = 8}
res_icov <- dplyr::filter(res, grepl("^informative", setting), grepl("N\\(0, 1\\)", dist))
res_icov <- tidyr::complete(res_icov, setting, Method, dist, key)

icov_fdr <- dplyr::filter(res_icov, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ setting, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDP", labels = scales::percent) +
    ggtitle("Mean FDP Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

gp <- plot_grid(icov_fdr + guides(color = FALSE, linetype = FALSE) + coord_cartesian(ylim = c(0, .2)),
                icov_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(icov_tpr), rel_widths = c(1, 1/16))
gp
```

@@

noni_fdr <- dplyr::filter(res_noni, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ dist, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDP", labels = scales::percent) +
    ggtitle("Mean FDP Over 100 Replications (noninformative covariates)") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

@@

compc_fdr <- dplyr::filter(res_compc, key == "FDR") %>%
    dplyr::select(setting, Method, dist, alpha, lab, mean_value) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, label = lab,
               color = Method, linetype = Method)) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    geom_hline(yintercept = c(.01, .1), lty = 2, color = "blue", alpha = 1/2) + 
    geom_vline(xintercept = c(.01, .1), lty = 2, color = "blue", alpha = 1/2) + 
    geom_line(alpha = 0.85) +
    geom_text(size = 3) + 
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("noninformative (FDP)", breaks = seq(0, 1, .02), labels = scales::percent) + 
    scale_y_continuous("informative (FDP)", breaks = seq(0, 1, .02), labels = scales::percent) + 
    ggtitle("Mean FDP Over 100 Replications") +
    expand_limits(x = 0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

```{r, fig.width = 10, fig.height = 4}
compc2_fdr <- dplyr::filter(res_compc, key == "FDR") %>%
    dplyr::select(setting, Method, dist, alpha, lab, mean_value) %>%
    tidyr::spread(setting, mean_value) %>%
    dplyr::mutate(gain = `informative-cubic` - noninformative) %>%
    ggplot(aes(x = alpha, y = gain, color = Method, linetype = Method)) +
    geom_hline(yintercept = 0, lty = 2, color = "blue", alpha = 1/2) + 
    geom_line(alpha = 0.85) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) + 
    scale_y_continuous("change in FDP", breaks = seq(-1, 1, .001), labels = scales::percent) + 
    ggtitle("Mean Change in FDP Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

pi0_fdr <- dplyr::filter(res_pi0, key == "FDR") %>%
    ggplot(aes(x = pi0, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 2.5, alpha=0.5) +
    geom_hline(aes(yintercept = alpha), lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ alpha, scales = "free_x", labeller = label_both) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("pi0", breaks = seq(0, 100, 10)) +
    scale_y_continuous("FDP", labels = scales::percent) +
    ggtitle("Mean FDP Over 100 Replications") +
    expand_limits(x =0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

info_fdr <- dplyr::filter(res_info, key == "FDR") %>%
    ggplot(aes(x = inform, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 2.5, alpha=0.5) +
    geom_hline(aes(yintercept = alpha), lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ alpha, scales = "free_x", labeller = label_both) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("informativeness", breaks = seq(0, 100, 10)) +
    scale_y_continuous("FDP", labels = scales::percent) +
    ggtitle("Mean FDP Over 100 Replications") +
    expand_limits(x =0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

dplyr::filter(res_uni, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(dist ~ signal, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDP", labels = scales::percent) +
    ggtitle("Mean FDP Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

uni_fdr <- dplyr::filter(res_uni, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_wrap(~ signal, scales = "free_x", label = label_both, nrow = 1) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDP", labels = scales::percent) +
    ggtitle("Mean FDP Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

>>>>

```{r, eval = FALSE}
for (ia in c(1:10, 20, 30, 40, 50)) {
    summary_file <- paste0("allres_alpha", ia, ".rds")
    if (!file.exists(summary_file)) {
        res_files <- list.files(path, "\\.rds$", full.names = TRUE)
        res <- lapply(res_files, function(x) {
            zz <- readRDS(x)
            zz <- plotsim_standardize(zz, alpha = ia / 100L)
            zz <- dplyr::select(zz, rep, blabel, key, alpha, value)
            zz <- dplyr::group_by(zz, blabel, key, alpha)
            zz <- dplyr::summarize(zz,
                                   se = sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))),
                                   q10 = quantile(value, .1, na.rm = TRUE),
                                   q90 = quantile(value, .9, na.rm = TRUE),
                                   med_value = median(value, na.rm = TRUE),
                                   mean_value = mean(value, na.rm = TRUE),
                                   nNA = sum(is.na(value)))
            dplyr::ungroup(zz)
        })
        names(res) <- gsub("\\.rds$", "", basename(res_files))
        saveRDS(res, summary_file)
    }
}
```

@@

```{r}
alphas <- 1:10
res <- vector("list", length(alphas))
for (ia in seq_len(length(alphas))) {
    imethodset <- methodset
    imethodset[which(imethodset == "ihw")] <- paste0("ihw-a", sprintf("%02d", alphas[ia]))
    ires <- readRDS(paste0("allres_alpha", alphas[ia], ".rds"))
    ires <- bind_rows(ires, .id = "setting")
    ires <- dplyr::mutate(ires, dist = gsub(".*?-benchmark-(.*)", "\\1", setting),
                         setting = gsub("(.*?)-benchmark-.*", "\\1", setting))
    ires <- dplyr::filter(ires, blabel %in% imethodset)
    ires <- dplyr::mutate(ires, blabel = gsub("(-a)(.*)", "", blabel))
    res[[ia]] <- ires
}
res <- bind_rows(res)
res <- dplyr::rename(res, Method = blabel)
res <- dplyr::mutate(res, Method = gsub("-df03", "", Method))
res <- dplyr::mutate(res, Method = factor(Method, levels = gsub("-df03", "", methodset)))
```

@@

noise_fdr <- dplyr::filter(res_noise, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ dist, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDR", labels = scales::percent) +
    ggtitle("Mean FDR Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

gp <- plot_grid(noise_fdr + guides(color = FALSE, linetype = FALSE),
                noise_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(noise_tpr), rel_widths = c(1, 1/16))
gp

@@

```{r, fig.width = 14, fig.height = 8}
res_icov <- dplyr::filter(res, grepl("^informative", setting), grepl("N\\(0, 1\\)", dist))
res_icov <- tidyr::complete(res_icov, setting, Method, dist, key)

icov_fdr <- dplyr::filter(res_icov, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ setting, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDR", labels = scales::percent) +
    ggtitle("Mean FDR Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

gp <- plot_grid(icov_fdr + guides(color = FALSE, linetype = FALSE),
                icov_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(icov_tpr), rel_widths = c(1, 1/12))
gp
```

@@

noni_fdr <- dplyr::filter(res_noni, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ dist, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDR", labels = scales::percent) +
    ggtitle("Mean FDR Over 100 Replications (noninformative covariates)") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

gp <- plot_grid(noni_fdr + guides(color = FALSE, linetype = FALSE),
                noni_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(noni_tpr), rel_widths = c(1, 1/16))
gp

@@

compc_fdr <- dplyr::filter(res_compc, key == "FDR") %>%
    dplyr::select(setting, Method, dist, alpha, lab, mean_value) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, label = lab,
               color = Method, linetype = Method)) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    geom_hline(yintercept = c(.01, .1), lty = 2, color = "blue", alpha = 1/2) + 
    geom_vline(xintercept = c(.01, .1), lty = 2, color = "blue", alpha = 1/2) + 
    geom_line(alpha = 0.85) +
    geom_text(size = 3) + 
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("noninformative (FDR)", breaks = seq(0, 1, .02), labels = scales::percent) + 
    scale_y_continuous("informative (FDR)", breaks = seq(0, 1, .02), labels = scales::percent) + 
    ggtitle("Mean FDR Over 100 Replications") +
    expand_limits(x = 0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

```{r, fig.width = 10, fig.height = 4}
compc2_fdr <- dplyr::filter(res_compc, key == "FDR") %>%
    dplyr::select(setting, Method, dist, alpha, lab, mean_value) %>%
    tidyr::spread(setting, mean_value) %>%
    dplyr::mutate(gain = `informative-cubic` - noninformative) %>%
    ggplot(aes(x = alpha, y = gain, color = Method, linetype = Method)) +
    geom_hline(yintercept = 0, lty = 2, color = "blue", alpha = 1/2) + 
    geom_line(alpha = 0.85) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) + 
    scale_y_continuous("change in FDR", breaks = seq(-1, 1, .001), labels = scales::percent) + 
    ggtitle("Mean Change in FDR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

pi0_fdr <- dplyr::filter(res_pi0, key == "FDR") %>%
    ggplot(aes(x = pi0, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 2.5, alpha=0.5) +
    geom_hline(aes(yintercept = alpha), lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ alpha, scales = "free_x", labeller = label_both) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("pi0", breaks = seq(0, 100, 10)) +
    scale_y_continuous("FDR", labels = scales::percent) +
    ggtitle("Mean FDR Over 100 Replications") +
    expand_limits(x =0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

info_fdr <- dplyr::filter(res_info, key == "FDR") %>%
    ggplot(aes(x = inform, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 2.5, alpha=0.5) +
    geom_hline(aes(yintercept = alpha), lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ alpha, scales = "free_x", labeller = label_both) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("informativeness", breaks = seq(0, 100, 10)) +
    scale_y_continuous("FDR", labels = scales::percent) +
    ggtitle("Mean FDR Over 100 Replications") +
    expand_limits(x =0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

dplyr::filter(res_uni, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(dist ~ signal, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDR", labels = scales::percent) +
    ggtitle("Mean FDR Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

uni_fdr <- dplyr::filter(res_uni, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_wrap(~ signal, scales = "free_x", label = label_both, nrow = 1) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDR", labels = scales::percent) +
    ggtitle("Mean FDR Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

@@

# ASH unimodality

```{r}
alphas50 <- c(5, 10, 20, 30, 40, 50)
res_fdr50 <- vector("list", length(alphas50))
for (ia in seq_len(length(alphas50))) {
    imethodset <- methodset
    imethodset[which(imethodset == "ihw")] <- "ihw-a10"
    ires <- readRDS(paste0("allres_alpha", alphas50[ia], ".rds"))
    ires <- bind_rows(ires, .id = "setting")
    ires <- dplyr::mutate(ires, dist = gsub(".*?-benchmark-(.*)", "\\1", setting),
                         setting = gsub("(.*?)-benchmark-.*", "\\1", setting))
    ires <- dplyr::filter(ires, blabel %in% imethodset)
    ires <- dplyr::mutate(ires, blabel = gsub("(-a)(.*)", "", blabel))
    res_fdr50[[ia]] <- ires
}
res_fdr50 <- bind_rows(res_fdr50)
res_fdr50 <- dplyr::rename(res_fdr50, Method = blabel)
res_fdr50 <- dplyr::mutate(res_fdr50, Method = gsub("-df03", "", Method))
res_fdr50 <- dplyr::mutate(res_fdr50, Method = factor(Method, levels = gsub("-df03", "", methodset)))
```

```{r}
res_fdr50 <- dplyr::mutate(res_fdr50, inform = ifelse(grepl("varyinginfo", setting), dist, NA))
res_fdr50 <- dplyr::mutate(res_fdr50, inform = as.numeric(gsub("level", "", inform)))
res_fdr50 <- dplyr::mutate(res_fdr50, dist = ifelse(grepl("varyinginfo", setting), "gaussian", dist))

res_fdr50 <- dplyr::mutate(res_fdr50, pi0 = ifelse(grepl("varyingpi0", setting), dist, 90))
res_fdr50 <- dplyr::mutate(res_fdr50, pi0 = as.numeric(gsub("nullprop", "", pi0)))
res_fdr50 <- dplyr::mutate(res_fdr50, dist = ifelse(grepl("varyingpi0", setting), "gaussian", dist))

res_fdr50 <- dplyr::mutate(res_fdr50, signal = ifelse(grepl("varyinges", setting), dist, NA))
res_fdr50 <- dplyr::mutate(res_fdr50, dist = ifelse(grepl("^varyinges$", setting), "gaussian", dist))
res_fdr50 <- dplyr::mutate(res_fdr50, dist = ifelse(grepl("^varyinges-t$", setting), "t11", dist))
res_fdr50 <- dplyr::mutate(res_fdr50, dist = ifelse(grepl("^varyinges-chisq$", setting), "chisq4", dist))
res_fdr50 <- dplyr::mutate(res_fdr50, setting = ifelse(grepl("varyinges", setting), "varyinges", setting))
```

```{r}
res_fdr50 <- dplyr::mutate(res_fdr50, dist = factor(dist, levels = c("gaussian", "t11", "t5", "chisq4"),
                                                    labels = c(expression("Noise: " * N(0, 1)),
                                                               expression("Noise: " * t[11]),
                                                               expression("Noise: " * t[5]),
                                                               expression("Noise: " * {chi^2}[4]))))
```

We take a look at the unimodal set of simulations with Normal sampling noise.

```{r, fig.width = 18, fig.height = 8}
res50_uni <- dplyr::filter(res_fdr50, setting == "varyinges", grepl("N\\(0, 1\\)", dist))
res50_uni <- dplyr::mutate(res50_uni, dist = droplevels(dist))
res50_uni <- tidyr::complete(res50_uni, Method, signal, dist, key)

uni50_fdr <- dplyr::filter(res50_uni, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_wrap(~ signal, scales = "free_x", label = label_both, nrow = 1) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .1)) +
    scale_y_continuous("FDR", labels = scales::percent) +
    ggtitle("Mean FDR Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

uni50_tpr <- dplyr::filter(res50_uni, key == "TPR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.025, alpha=0.5) +
    facet_wrap(~ signal, scales = "free", label = label_both, nrow = 1) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .1)) +
    scale_y_continuous("TPR", labels = scales::percent) +
    ggtitle("Mean TPR Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

gp <- plot_grid(uni50_fdr + guides(color = FALSE, linetype = FALSE),
                uni50_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(uni50_tpr), rel_widths = c(1, 1/16))
gp
```

# Figure Sim1

We combine some of the results from above into a single figure.

```{r, fig.width = 10, fig.height = 11}
## Figure Sim1, PanelA: FDR under different sampling distributions

## Figure Sim1, PanelB: informativeness, FDR at alpha = 0.10
fs1b <- dplyr::filter(res_info, key == "FDR", alpha == 0.10) %>%
    ggplot(aes(x = inform, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 2.5, alpha=0.5) +
    geom_hline(aes(yintercept = alpha), lty = 2, color = "blue", alpha = 1/2) + 
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("informativeness", breaks = seq(0, 100, 10)) +
    scale_y_continuous("FDR", labels = scales::percent) +
    ggtitle("Mean FDR Over 100 Replications") +
    expand_limits(x =0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

## Figure Sim1, PanelC: informativeness, TPR at alpha = 0.10
fs1c <- dplyr::filter(res_info, key == "TPR", alpha == 0.10) %>%
    ggplot(aes(x = inform, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 2.5, alpha=0.5) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("informativeness", breaks = seq(0, 100, 10)) +
    scale_y_continuous("TPR", labels = scales::percent) +
    ggtitle("Mean TPR Over 100 Replications") +
    expand_limits(x =0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

## Figure Sim1, PanelD: varying null proportions, FDR at alpha = 0.10
fs1d <- dplyr::filter(res_pi0, key == "FDR", alpha == 0.10) %>%
    ggplot(aes(x = pi0, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 2.5, alpha=0.5) +
    geom_hline(aes(yintercept = alpha), lty = 2, color = "blue", alpha = 1/2) + 
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("pi0", breaks = seq(0, 100, 10)) +
    scale_y_continuous("FDR", labels = scales::percent) +
    ggtitle("Mean FDR Over 100 Replications") +
    expand_limits(x =0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

## Figure Sim1, PanelE: varying null proportions, TPR at alpha = 0.10
fs1e <- dplyr::filter(res_pi0, key == "TPR", alpha == 0.10) %>%
    ggplot(aes(x = pi0, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 2.5, alpha=0.5) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("pi0", breaks = seq(0, 100, 10)) +
    scale_y_continuous("TPR", labels = scales::percent) +
    ggtitle("Mean TPR Over 100 Replications") +
    expand_limits(x =0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

gp <- plot_grid(fs1b + guides(color = FALSE, linetype = FALSE),
                fs1c + guides(color = FALSE, linetype = FALSE),
                fs1d + guides(color = FALSE, linetype = FALSE),
                fs1e + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[2:5], ncol = 2)
gp <- plot_grid(gp, get_legend(fs1b), rel_widths = c(1, 1/8))
plot_grid(noise_fdr + guides(color = FALSE, linetype = FALSE) + coord_cartesian(ylim = c(0, .2)),
          gp, ncol = 1, rel_heights = c(5/12, 1),
          labels = c(LETTERS[1], NA))
```
